#Python code to download NBA shotchart data
#Below is for the regular season 2015-16 as an example

from nba_api.stats.endpoints import shotchartdetail
import json
import pandas as pd

response = shotchartdetail.ShotChartDetail(
    team_id=0,
    player_id=0,
    context_measure_simple = 'FGA', 
    season_nullable='2015-16',
    season_type_all_star='Regular Season'
)

content = json.loads(response.get_json())

results = content['resultSets'][0]
headers = results['headers']
rows = results['rowSet']
df = pd.DataFrame(rows)
df.columns = headers

# write to csv file
df.to_csv('D:\\nba_2015_16.csv', index=False)



```{r}
## Input the year you want to work on, this is the only input needed.
year = "2015-16"
```

```{r}
library(rTensor)
library(einsum)
library(stats)
library(qlcMatrix)
library(pracma)
library(arm)
library(CHNOSZ)
library(parallel)
library(dTBM)
library(torch)
library(Matrix)
library(dplyr)
library(openxlsx)

options(warn=-1)

## read in shot chart data as rawdata
rawdata=read.csv(paste0("nba_",year,".csv"), sep=",", header=T)

## only retain players having at least 400 shots and only shots in regular quarters and store as data
mytable = table(rawdata$PLAYER_ID, rawdata$SHOT_ATTEMPTED_FLAG) # count the number of attempts by players
player.set=as.numeric(row.names(as.data.frame(mytable[mytable>399,])))
data=rawdata[rawdata$PLAYER_ID %in% player.set,]  
data=data[data$PERIOD< 5,] # only consider regular quarters

## divide and label the front court into 18 zones and store in data
temploc=count(rawdata, SHOT_ZONE_AREA, SHOT_ZONE_RANGE, SHOT_ZONE_BASIC, SHOT_ATTEMPTED_FLAG)
temploc=temploc[temploc$SHOT_ZONE_AREA !="Back Court(BC)",]
temploc$zone=c(5,6,3,4,2,1,7,8,11,12,9,10,13,14,17,18,15,16)
data <- (merge(data, temploc, by = c('SHOT_ZONE_BASIC', 'SHOT_ZONE_AREA', 'SHOT_ZONE_RANGE')))

## create three variables
data$z1=data$MINUTES_REMAINING+data$SECONDS_REMAINING/60 # create time remaining variable
data$z2=data$SHOT_DISTANCE # create shot distance varaible
tnames=sort(unique(data$TEAM_NAME))
tcodes=c("ATL", "BOS", "BKN", "CHA", "CHI", "CLE", "DAL", "DEN", "DET", "GSW", "HOU", "IND", "LAC", "LAL", "MEM", "MIA", "MIL", "MIN", "NOP", "NYK", "OKC", "ORL", "PHI", "PHX", "POR", "SAC", "SAS", "TOR", "UTA", "WAS")
tname.code=cbind(tnames,tcodes)
colnames(tname.code)=c("TEAM_NAME", "TEAM_CODE")
data=merge(data,tname.code, by=c("TEAM_NAME"))
data$z3=ifelse(data$TEAM_CODE==data$HTM,1,0) ## create home team dummy

## create data1 to prepare for mytensor.Y and data.shot as input to main algorithm
data1=data.frame(data$PLAYER_ID, data$PERIOD, data$zone, data$SHOT_MADE_FLAG, data$z1, data$z2, data$z3, data$PLAYER_NAME)

## create mytensor.Y as the 3-mode tensor counts for the model
mytensor.Y=array(rep(0, (length(player.set)*4*18)),dim=c(length(player.set),4,18)) # attempts
data1=cbind(data1,rep(0,nrow(data1)))
for(i in 1:nrow(data1)){
  dim1=which(player.set==data1[i,1])
  dim2=data1[i,2]
  dim3=data1[i,3]
  data1[i,9]=dim1
  mytensor.Y[dim1,dim2,dim3]=mytensor.Y[dim1,dim2,dim3]+1
}

## create data.shot to store the responses and covariate values per shot for the logistic regression
ones=rep(1,nrow(data1))
data.shot=cbind(data1$`rep(0, nrow(data1))`, data1$data.PERIOD, data1$data.zone,  data1$data.SHOT_MADE_FLAG, data1$data.z1, data1$data.z2, data1$data.z3, ones)
colnames(data.shot)=c("dim1","dim2","dim3","made","min_left","distance","Home", "intercept")
data.shot=data.shot[order(data.shot[,1],data.shot[,3],data.shot[,2]),]

```











